Projection variability of clausal complements across different operators

### 2023-09-18 talks/XPrag-poster/xprag-poster.tex
abbreviated references

			\vspace{\vboxsep}
			\begin{normalbox}{\phantom.\hfill Existing theories of projection do not predict our results}
				\centering
				\begin{theorybox}{Dynamic accounts of projection: Lexical triggering + dynamic semantics \hfill (\citealt{heim_projection_1983,van_der_sandt_presupposition_1992})}
					\small Distinguish factive and non-factive predicates:
					\vspace{-.3\baselineskip}
					\begin{itemize}
						\item \underline{factive} predicates (\textit{be annoyed, regret, \dots}): CC conventionally required to be contextually entailed in common ground
						\item \underline{non-factive} predicates (\textit{believe, say, …}): no such requirement
					\end{itemize}
					\vspace{-.2\baselineskip}
					Factive content projects globally, unless not admitted by common ground
				\end{theorybox}

@@

				\textbf{Márta Abrusán}. Predicting the presuppositions of soft triggers. \textit{Linguistics and philosophy}, 34:491–535, 2011.\quad\textbullet\quad
				%
				\textbf{Gennaro Chierchia and Sally McConnell-Ginet.} \textit{Meaning and grammar: An introduction to semantics.} 1990.\quad\textbullet\quad
				%
				\textbf{Elizabeth Coppock and Lucas Champollion.} \textit{Invitation to formal semantics.} online publication, in progress, 2020.\quad\textbullet\quad
				%
				\textbf{Marie de Marneffe, Mandy Simons, and Judith Tonhauser.} The CommitmentBank: Investigating projection in naturally occurring discourse. \textit{Sinn und Bedeutung}, 23:107–124, 2019.\quad\textbullet\quad
				%
				\textbf{Marie-Catherine de Marneffe, Christopher D. Manning, and Christopher Potts.} Did It Happen? The Pragmatic Complexity of Veridicality Assessment. \textit{Computational Linguistics}, 38(2):301–333, February 2012.\quad\textbullet\quad
				%
				\textbf{Judith Degen and Judith Tonhauser.} Prior beliefs modulate projection. \textit{Open Mind}, 5:59–70, 2021.\quad\textbullet\quad
				%
				\textbf{Judith Degen and Judith Tonhauser.} Are there factive predicates? An empirical investigation. \textit{Language}, 98(3):552–591, 2022.\quad\textbullet\quad
				%
				\textbf{Kajsa Djärv and Hezekiah Akiva Bacovcin.} Prosodic effects on factive presupposition projection. \textit{Semantics and Linguistic Theory}, 27:116–133, 2017.\quad\textbullet\quad
				%
				\textbf{Tom Roberts.} I can’t believe it’s not lexical: Deriving distributed veridicality. Semantics and Linguistic Theory, \textit{Semantics and Linguistic Theory}, 29:665–685, 2019.\quad\textbullet\quad
				%
				\textbf{Gottlob Frege.} Über Sinn und Bedeutung. \textit{Zeitschrift für Philosophie und philosophische Kritik}, pages 25–50, 1892.\quad\textbullet\quad
				%
				\textbf{Irene Heim.} On the projection problem for presuppositions. \textit{Formal semantics–the essential readings}, pages 249–260, 1983.\quad\textbullet\quad
				%
				\textbf{Lauri Karttunen.} Some observations on factivity. \textit{Research on Language \& Social Interaction}, 4(1):55–69, 1971.\quad\textbullet\quad
				%
				\textbf{Lauri Karttunen and Stanley Peters.} Conventional implicature. In Choon-Kyu Oh and David A. Dinneen, editors, \textit{Presuppositions, Syntax and Semantics} Vol.11, pages 1–56. New York: Academic Press, 1979.\quad\textbullet\quad
				%
				\textbf{Paul Kiparsky and Carol Kiparsky.} Fact. In Manfred Bierwisch and Karl Erich Heidolph, editors, \textit{Progress in Linguistics}, pages 143–173. The Hague: Mouton, 1970.\quad\textbullet\quad
				%
				\textbf{Taylor Mahler.} The social component of projection behavior of clausal complements. \textit{Linguistic Society of America}, 5:777–791, 2020.\quad\textbullet\quad
				%
				\textbf{Philippe Schlenker.} Triggering presuppositions. \textit{Glossa: a journal of general linguistics}, 6(1), 2021.\quad\textbullet\quad
				%
				\textbf{Judith Sieker and Torgrim Solstad.} Projective variability of (semi) factive verbs in family of sentence contexts: A rating study. \textit{In Proceedings of the 23rd Amsterdam Colloquium}, 2022.\quad\textbullet\quad
				%
				\textbf{Mandy Simons, David Beaver, Craige Roberts, and Judith Tonhauser.} The best question: Explaining the projection behavior of factives. \textit{Discourse processes}, 54(3):187–206, 2017.\quad\textbullet\quad
				%
				\textbf{E. Allyn Smith and Kathleen Currie Hall.} The relationship between projection and embedding environment. \textit{In Proceedings of the 48th Meeting of the Chicago Linguistics Society}. 2014.\quad\textbullet\quad
				%
				\textbf{Peter F. Strawson.} On referring. \textit{Mind}, 59(235):320–344, 1950.\quad\textbullet\quad
				%
				\textbf{Judith Tonhauser.} Prosodic cues to presupposition projection. In \textit{Semantics and Linguistic Theory}, volume 26, pages 934–960, 2016.\quad\textbullet\quad
				%
				\textbf{Judith Tonhauser, David I. Beaver, and Judith Degen.} How projective is projective content? Gradience in projectivity and at-issueness. \textit{Journal of Semantics}, 35(3):495–542, 2018.\quad\textbullet\quad
				%
				\textbf{Rob A. van der Sandt.} Presupposition projection as anaphora resolution. \textit{Journal of semantics}, 9(4):333–377, 1992.

>>>>

			\vspace{\vboxsep}
			\begin{normalbox}{\phantom.\hfill Existing theories of projection do not predict our results}
				\centering
				\begin{theorybox}{Dynamic accounts of projection: Lexical triggering + dynamic semantics \hfill (\citealt{heim_presupposition_1992,van_der_sandt_presupposition_1992})}
					\small Distinguish factive and non-factive predicates:
					\vspace{-.3\baselineskip}
					\begin{itemize}
						\item \underline{factive} predicates (\textit{be annoyed, regret, \dots}): CC conventionally required to be contextually entailed in common ground
						\item \underline{non-factive} predicates (\textit{believe, say, …}): no such requirement
					\end{itemize}
					\vspace{-.2\baselineskip}
					Factive content projects globally, unless not admitted by common ground
				\end{theorybox}

@@

				\textbf{Márta Abrusán}. Predicting the presuppositions of soft triggers. \textit{L\&P}, 2011.\quad\textbullet\quad
				%
				\textbf{Gennaro Chierchia and Sally McConnell-Ginet.} \textit{Meaning and grammar: An introduction to semantics.} 1990.\quad\textbullet\quad
				%
				\textbf{Elizabeth Coppock and Lucas Champollion.} \textit{Invitation to formal semantics.} 2020.\quad\textbullet\quad
				%
				\textbf{Marie de Marneffe, Mandy Simons, and Judith Tonhauser.} The CommitmentBank: Investigating projection in naturally occurring discourse. \textit{SuB}, 2019.\quad\textbullet\quad
				%
				\textbf{Marie-Catherine de Marneffe, Christopher D. Manning, and Christopher Potts.} Did It Happen? The Pragmatic Complexity of Veridicality Assessment. \textit{Comp. Ling.}, February 2012.\quad\textbullet\quad
				%
				\textbf{Judith Degen and Judith Tonhauser.} Prior beliefs modulate projection. \textit{Open Mind}, 2021.\quad\textbullet\quad
				%
				\textbf{Judith Degen and Judith Tonhauser.} Are there factive predicates? An empirical investigation. \textit{Language}, 2022.\quad\textbullet\quad
				%
				\textbf{Kajsa Djärv and Hezekiah Akiva Bacovcin.} Prosodic effects on factive presupposition projection. \textit{SALT}, 2017.\quad\textbullet\quad
				%
				\textbf{Tom Roberts.} I can’t believe it’s not lexical: Deriving distributed veridicality. Semantics and Linguistic Theory, \textit{SALT}, 2019.\quad\textbullet\quad
				%
				\textbf{Gottlob Frege.} Über Sinn und Bedeutung. \textit{Zeitschrift für Philosophie und philosophische Kritik}, 1892.\quad\textbullet\quad
				%
				\textbf{Irene Heim.} Presupposition projection and the semantics of attitude verbs. \textit{JoS},1992.\quad\textbullet\quad
				%
				\textbf{Lauri Karttunen.} Some observations on factivity. \textit{Research on Language \& Social Interaction}, 1971.\quad\textbullet\quad
				%
				\textbf{Lauri Karttunen and Stanley Peters.} Conventional implicature. In Choon-Kyu Oh and David A. Dinneen, eds., \textit{Presuppositions, Syntax and Semantics}, 1979.\quad\textbullet\quad
				%
				\textbf{Paul Kiparsky and Carol Kiparsky.} Fact. In Manfred Bierwisch and Karl Erich Heidolph, eds., \textit{Progress in Linguistics}, 1970.\quad\textbullet\quad
				%
				\textbf{Taylor Mahler.} The social component of projection behavior of clausal complements. \textit{LSA}, 2020.\quad\textbullet\quad
				%
				\textbf{Philippe Schlenker.} Triggering presuppositions. \textit{Glossa}, 2021.\quad\textbullet\quad
				%
				\textbf{Judith Sieker and Torgrim Solstad.} Projective variability of (semi) factive verbs in family of sentence contexts: A rating study. \textit{AC 23}, 2022.\quad\textbullet\quad
				%
				\textbf{Mandy Simons, David Beaver, Craige Roberts, and Judith Tonhauser.} The best question: Explaining the projection behavior of factives. \textit{Discourse processes}, 2017.\quad\textbullet\quad
				%
				\textbf{E. Allyn Smith and Kathleen Currie Hall.} The relationship between projection and embedding environment. \textit{CLS 48}. 2014.\quad\textbullet\quad
				%
				\textbf{Peter F. Strawson.} On referring. \textit{Mind}, 1950.\quad\textbullet\quad
				%
				\textbf{Judith Tonhauser.} Prosodic cues to presupposition projection. In \textit{SALT}, 2016.\quad\textbullet\quad
				%
				\textbf{Judith Tonhauser, David I. Beaver, and Judith Degen.} How projective is projective content? Gradience in projectivity and at-issueness. \textit{JoS}, 2018.\quad\textbullet\quad
				%
				\textbf{Rob A. van der Sandt.} Presupposition projection as anaphora resolution. \textit{JoS}, 1992.
